The Spine of American Legal Practice

### 2016-06-28 article/article.Rmd
Revisions to clustering sections
Cite the macroscope

The computational evidence that we assembled revealed patterns in how law migrated at several different scales of analysis. We used the similarity matrix as the input to three different digital history techniques: network analysis, visualizations, and clustering.

@@

## Appendix: Clustering sections involving racial exclusions from witness testimony

>>>>

The computational evidence that we assembled revealed patterns in how law migrated at several different scales of analysis.^[Our attention to big and small scales is the main aim described in Shawn Graham, Ian Milligan, and Scott Weingart, *Exploring Big Historical Data: The Historian’s Macroscope* (Imperial College Press, 2015).] We used the similarity matrix as the input to three different digital history techniques: network analysis, visualizations, and clustering.

@@

## Appendix: Clustering sections involving witness exclusions

This sample cluster brings together sections that involve racial exclusions from witness testimony in civil trials, with commentary.
